---
title: "Correlations"
author: "Cecile C. Remy"
date: "April 2, 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
These codes produce the results of figure 5 and figure S4.
The files used are located in the folder named "Correlations" and contain the data (charcoal measurements, fire histories, pollen percentages, PAR, and mean July temperature) based on the outputs created to produce the figures and results for each site (Rosalia_corr.txt, Rosalia_corr_charcoal.txt, and Pikku_corr.txt, Pikku_charcoal.txt). 

```{r}
#install.packages("ggplot2") #if not already installed
library("ggplot2")
windowsFonts(Times=windowsFont("Times New Roman"))
#install.packages("ggridges") #if not already installed
library(ggridges)
#install.packages("reshape2") #if not already installed
library(reshape2)
#install.packages("viridis") #if not already installed
library(viridis)
#install.packages("gridExtra") #if not already installed
library(gridExtra)
```

```{r}
dirs<-c('Correlations/')
Files<-list.files(dirs)

Pikku_charcoal<-read.table("Correlations/Pikku_corr_charcoal.txt",head=T,sep=" ")
Rosalia_charcoal<-read.table("Correlations/Rosalia_corr_charcoal.txt",head=T,sep=" ")
Pikku_Fire<-read.table("Correlations/Pikku_corr.txt",head=T,sep=" ")
Rosalia_Fire<-read.table("Correlations/Rosalia_corr.txt",head=T,sep=" ")
```
##Rosalia
```{r}
           
BB<-data.frame()
FF<-data.frame()
FS<-data.frame()
TJ<-data.frame()
for (u in 1:999){  #number of iterations
COL_BB<-c(6:18)
COL_FF<-c(6:18)
COL_FS<-c(6:18)
COL_TJ<-c(6:18)
x<-Rosalia_charcoal[sample(nrow(Rosalia_charcoal), 110), ]
for (i in 1:13){
BB_x<-cor.test(x[,COL_BB[i]],x[,2], method = c("pearson"))$estimate[[1]]
FF_x<-cor.test(x[,COL_FF[i]],x[,3], method = c("pearson"))$estimate[[1]]
FS_x<-cor.test(x[,COL_FS[i]],x[,4], method = c("pearson"))$estimate[[1]]
TJ_x<-cor.test(x[,COL_TJ[i]],x[,5], method = c("pearson"))$estimate[[1]]

BB[u,i]<-BB_x
FF[u,i]<-FF_x
FS[u,i]<-FS_x
TJ[u,i]<-TJ_x
}
}

colnames(BB)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
colnames(FF)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
colnames(FS)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")  
colnames(TJ)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
BB[is.na(BB)] <- 0
FF[is.na(FF)] <- 0
FS[is.na(FS)] <- 0
TJ[is.na(TJ)] <- 0

LW<-data.frame()
for (u in 1:999){  #number of iterations
COL_LW<-c(2:5,8:20)
x<-Rosalia_Fire[sample(nrow(Rosalia_Fire), 84), ]
for (i in 1:17){
LW_x<-cor.test(x[,COL_LW[i]],x[,6], method = c("pearson"))$estimate[[1]]
LW[u,i]<-LW_x
}
}
  
colnames(LW)<-c("Biomass burned","Fire frequency","Fire size","July temperature","Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")

LW[is.na(LW)] <- 0

BB_plot<-t(BB)
BB_plot<-data.frame(rownames(BB_plot),BB_plot)
BB_plot<-melt(BB_plot,by="rownames.BB_plot.")
colnames(BB_plot)[1]<-'Species'
BB_plot$Species<-factor(BB_plot$Species,levels=rev(colnames(BB)))

FF_plot<-t(FF)
FF_plot<-data.frame(rownames(FF_plot),FF_plot)
FF_plot<-melt(FF_plot,by="rownames.FF_plot.")
colnames(FF_plot)[1]<-'Species'
FF_plot$Species<-factor(FF_plot$Species,levels=rev(colnames(FF)))

FS_plot<-t(FS)
FS_plot<-data.frame(rownames(FS_plot),FS_plot)
FS_plot<-melt(FS_plot,by="rownames.FS_plot.")
colnames(FS_plot)[1]<-'Species'
FS_plot$Species<-factor(FS_plot$Species,levels=rev(colnames(FS)))

LW_plot<-t(LW)
LW_plot<-data.frame(rownames(LW_plot),LW_plot)
LW_plot<-melt(LW_plot,by="rownames.LW_plot.")
colnames(LW_plot)[1]<-'Species'
LW_plot$Species<-factor(LW_plot$Species,levels=rev(colnames(LW)))

TJ_plot<-t(TJ)
TJ_plot<-data.frame(rownames(TJ_plot),TJ_plot)
TJ_plot<-melt(TJ_plot,by="rownames.TJ_plot.")
colnames(TJ_plot)[1]<-'Species'
TJ_plot$Species<-factor(TJ_plot$Species,levels=rev(colnames(TJ)))

RosBB_plot<-BB_plot
RosFF_plot<-FF_plot
RosFS_plot<-FS_plot
RosLW_plot<-LW_plot
RosTJ_plot<-TJ_plot
```

```{r}
#Pikku         
BB<-data.frame()
FF<-data.frame()
FS<-data.frame()
TJ<-data.frame()
for (u in 1:999){  #number of iterations
COL_BB<-c(6:18)
COL_FF<-c(6:18)
COL_FS<-c(6:18)
COL_TJ<-c(6:18)
x<-Pikku_charcoal[sample(nrow(Pikku_charcoal), 108), ]
for (i in 1:13){
BB_x<-cor.test(x[,COL_BB[i]],x[,2], method = c("pearson"))$estimate[[1]]
FF_x<-cor.test(x[,COL_FF[i]],x[,3], method = c("pearson"))$estimate[[1]]
FS_x<-cor.test(x[,COL_FS[i]],x[,4], method = c("pearson"))$estimate[[1]]
TJ_x<-cor.test(x[,COL_TJ[i]],x[,5], method = c("pearson"))$estimate[[1]]

BB[u,i]<-BB_x
FF[u,i]<-FF_x
FS[u,i]<-FS_x
TJ[u,i]<-TJ_x
}
}

colnames(BB)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
colnames(FF)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
colnames(FS)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")  
colnames(TJ)<-c("Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")
BB[is.na(BB)] <- 0
FF[is.na(FF)] <- 0
FS[is.na(FS)] <- 0
TJ[is.na(TJ)] <- 0

LW<-data.frame()
for (u in 1:999){  #number of iterations
COL_LW<-c(2:5,8:20)
x<-Pikku_Fire[sample(nrow(Pikku_Fire), 92), ]
for (i in 1:17){
LW_x<-cor.test(x[,COL_LW[i]],x[,6], method = c("pearson"))$estimate[[1]]
LW[u,i]<-LW_x
}
}
  
colnames(LW)<-c("Biomass burned","Fire frequency","Fire size","July temperature","Pinus","Picea","Betula","Alnus","Juniperus","Salix","Ericaceae","Poaceae","Artemisia","Cyperaceae","Sphagnum","PAR","ROC")

LW[is.na(LW)] <- 0

BB_plot<-t(BB)
BB_plot<-data.frame(rownames(BB_plot),BB_plot)
BB_plot<-melt(BB_plot,by="rownames.BB_plot.")
colnames(BB_plot)[1]<-'Species'
BB_plot$Species<-factor(BB_plot$Species,levels=rev(colnames(BB)))

FF_plot<-t(FF)
FF_plot<-data.frame(rownames(FF_plot),FF_plot)
FF_plot<-melt(FF_plot,by="rownames.FF_plot.")
colnames(FF_plot)[1]<-'Species'
FF_plot$Species<-factor(FF_plot$Species,levels=rev(colnames(FF)))

FS_plot<-t(FS)
FS_plot<-data.frame(rownames(FS_plot),FS_plot)
FS_plot<-melt(FS_plot,by="rownames.FS_plot.")
colnames(FS_plot)[1]<-'Species'
FS_plot$Species<-factor(FS_plot$Species,levels=rev(colnames(FS)))

LW_plot<-t(LW)
LW_plot<-data.frame(rownames(LW_plot),LW_plot)
LW_plot<-melt(LW_plot,by="rownames.LW_plot.")
colnames(LW_plot)[1]<-'Species'
LW_plot$Species<-factor(LW_plot$Species,levels=rev(colnames(LW)))

TJ_plot<-t(TJ)
TJ_plot<-data.frame(rownames(TJ_plot),TJ_plot)
TJ_plot<-melt(TJ_plot,by="rownames.TJ_plot.")
colnames(TJ_plot)[1]<-'Species'
TJ_plot$Species<-factor(TJ_plot$Species,levels=rev(colnames(TJ)))

PikBB_plot<-BB_plot
PikFF_plot<-FF_plot
PikFS_plot<-FS_plot
PikLW_plot<-LW_plot
PikTJ_plot<-TJ_plot
```
##Graphs
```{r,fig.width=5,fig.height=10}
RosBB_plot<-cbind(rep(1,nrow(RosBB_plot)),RosBB_plot)
colnames(RosBB_plot)[1]<-"Site"
RosFF_plot<-cbind(rep(1,nrow(RosFF_plot)),RosFF_plot)
colnames(RosFF_plot)[1]<-"Site"
RosFS_plot<-cbind(rep(1,nrow(RosFS_plot)),RosFS_plot)
colnames(RosFS_plot)[1]<-"Site"
RosLW_plot<-cbind(rep(1,nrow(RosLW_plot)),RosLW_plot)
colnames(RosLW_plot)[1]<-"Site"
RosTJ_plot<-cbind(rep(1,nrow(RosTJ_plot)),RosTJ_plot)
colnames(RosTJ_plot)[1]<-"Site"

PikBB_plot<-cbind(rep(2,nrow(PikBB_plot)),PikBB_plot)
colnames(PikBB_plot)[1]<-"Site"
PikFF_plot<-cbind(rep(2,nrow(PikFF_plot)),PikFF_plot)
colnames(PikFF_plot)[1]<-"Site"
PikFS_plot<-cbind(rep(2,nrow(PikFS_plot)),PikFS_plot)
colnames(PikFS_plot)[1]<-"Site"
PikLW_plot<-cbind(rep(2,nrow(PikLW_plot)),PikLW_plot)
colnames(PikLW_plot)[1]<-"Site"
PikTJ_plot<-cbind(rep(2,nrow(PikTJ_plot)),PikTJ_plot)
colnames(PikTJ_plot)[1]<-"Site"

ComBB<-rbind(RosBB_plot,PikBB_plot)
ComBB$Site<-factor(ComBB$Site,labels=c("Rosalia","Pikku"))
ComFF<-rbind(RosFF_plot,PikFF_plot)
ComFF$Site<-factor(ComFF$Site,labels=c("Rosalia","Pikku"))
ComFS<-rbind(RosFS_plot,PikFS_plot)
ComFS$Site<-factor(ComFS$Site,labels=c("Rosalia","Pikku"))
ComLW<-rbind(RosLW_plot,PikLW_plot)
ComLW$Site<-factor(ComLW$Site,labels=c("Rosalia","Pikku"))
ComTJ<-rbind(RosTJ_plot,PikTJ_plot)
ComTJ$Site<-factor(ComTJ$Site,labels=c("Rosalia","Pikku"))

cols <-  alpha(c("Rosalia" = "gold3", "Pikku" = "lightseagreen"),0.4)

BB_p<-    
ggplot(ComBB,aes(x=value,y=Species,fill=Site))+
   theme_minimal()+
   geom_density_ridges_gradient(scale = 1, size = 0.3, rel_min_height = 0.01)+
   scale_fill_manual(values=cols)+
   scale_x_continuous(limits=c(-1,1))+
   geom_vline(xintercept = 0,linetype="dotted")+
   labs(title="Biomass burned")+
   theme(text=element_text(family="Times"),
   axis.title.y=element_blank(),
   axis.title.x=element_blank(),
   axis.text.y=element_text(face="italic"),
   axis.text.x=element_text())
BB_p
   
FF_p<-    
ggplot(ComFF,aes(x=value,y=Species,fill=Site))+
   theme_minimal()+
   geom_density_ridges_gradient(scale = 1, size = 0.3, rel_min_height = 0.01)+
   scale_fill_manual(values=cols)+
   scale_x_continuous(limits=c(-1,1))+
   geom_vline(xintercept = 0,linetype="dotted")+
   labs(title="Fire frequency")+
   theme(text=element_text(family="Times"),
   axis.title.y=element_blank(),
   axis.title.x=element_blank(),
   axis.text.y=element_text(face="italic"),
   axis.text.x=element_text())
FF_p
         
FS_p<-    
ggplot(ComFS,aes(x=value,y=Species,fill=Site))+
   theme_minimal()+
   geom_density_ridges_gradient(scale = 1, size = 0.3, rel_min_height = 0.01)+
   scale_fill_manual(values=cols)+
   scale_x_continuous(limits=c(-1,1))+
   geom_vline(xintercept = 0,linetype="dotted")+
   labs(title="Fire size")+
   theme(text=element_text(family="Times"),
   axis.title.y=element_blank(),
   axis.title.x=element_blank(),
   axis.text.y=element_text(face="italic"),
   axis.text.x=element_text())
FS_p

TJ_p<-    
ggplot(ComTJ,aes(x=value,y=Species,fill=Site))+
   theme_minimal()+
   geom_density_ridges_gradient(scale = 1, size = 0.3, rel_min_height = 0.01)+
   scale_fill_manual(values=cols)+
   scale_x_continuous(limits=c(-1,1))+
   geom_vline(xintercept = 0,linetype="dotted")+
   labs(title="July temperature")+
   theme(text=element_text(family="Times"),
   axis.title.y=element_blank(),
   axis.title.x=element_blank(),
   axis.text.y=element_text(face="italic"),
   axis.text.x=element_text())
TJ_p

LW_p<-    
ggplot(ComLW,aes(x=value,y=Species,fill=Site))+
   theme_minimal()+
   geom_density_ridges_gradient(scale = 1, size = 0.3, rel_min_height = 0.01)+
   scale_fill_manual(values=cols)+
   scale_x_continuous(limits=c(-1,1))+
   geom_vline(xintercept = 0,linetype="dotted")+
   labs(title="Portion of charcoal with wood aspect")+
   theme(text=element_text(family="Times"),
   axis.title.y=element_blank(),
   axis.title.x=element_blank(),
   axis.text.y=element_text(face="italic"),
   axis.text.x=element_text())
LW_p
         

```