---
title: "Fire_histories_watershed"
author: "Cecile C. Remy"
date: "April 2, 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
These codes produce the results of figure 4.
The files used are located in the folder named "Fire_histories" and contain the charcoal data: charcoal count interpolated from the age-depth models (named Count_Rosalia.csv and Count_Pikku.csv), the dates of the fire events (named Fire_events.csv) extracted from the CharAnalysis outputs, the individual charcoal measurements (Pikku_individual_charcoal.csv and Rosalia_individual_charcoal.csv) the outputs from the script named "Fire histories" which are the Biomass Burned at each site (BBRosalia.csv, BBPikku.csv) and averaged from the three sites (BB_Reg.csv), the Fire Frequency at each site and averaged from the three sites (FF_Reg.csv, which contains the data by site), and the Fire Size Index at each site and averaged from the three sites (FS_Reg.csv, which contains the data by site).

```{r }
#install.packages("ggplot2") #if not already installed
library("ggplot2")
windowsFonts(Times=windowsFont("Times New Roman"))
#install.packages("scales") #if not already installed
library("scales")
```

```{r}
dirs<-c('Fire_histories/')
Files<-list.files(dirs)
```
## **Rosalia**
# *Biomass burned*
```{r }
Char_Ros<-read.csv("Fire_histories/Count_Rosalia.csv",h=T,sep=";")[,c(3,4,6)]
colnames(Char_Ros)<-c("AgeTop","AgeBot","Count")

DF<-c()
for (i in 1:nrow(Char_Ros)){
Age<-seq(Char_Ros[i,1],Char_Ros[i,2],0.5)
CBind<-cbind(Age[1:c(length(Age)-1)],rep(Char_Ros[i,3],c(length(Age)-1)))
DF<-rbind(DF,CBind)
}
colnames(DF)<-c("Age","Count")

BB<-read.csv("Fire_histories/BB_Reg.csv",h=T,sep=",")
BB_Rosalia<-read.csv("Fire_histories/BBRosalia.csv",h=T,sep=",")[,c(1,2)]
colnames(BB_Rosalia)<-c("Age","MeanR")
BB_Rosalia$Age<-as.numeric(BB_Rosalia$Age)
BB_Rosalia[917:1118,2]<-NA

Ros_BBChar<-merge(DF,BB_Rosalia,by="Age")
Ros_BBChar<-na.omit(Ros_BBChar)

colnames(Ros_BBChar)<-c("Age","Count","Mean")
Ros_BBChar[,3]<-rescale(Ros_BBChar[,3], to=c(min(Ros_BBChar$Count),max(Ros_BBChar$Count)))
Ros_BBChar<-as.data.frame(Ros_BBChar)
Ros_BBChar$Age<-as.numeric(Ros_BBChar$Age)
mean(Ros_BBChar$Mean)

BBRosalia_plot<-
ggplot(data=Ros_BBChar,aes(x=Age))+
theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9052.5,32.5))+
   geom_line(aes(x=Age,y=Mean),size=1,color="red4")+
   geom_bar(aes(x=Age,y=Count),stat="identity", na.rm = TRUE)+
   geom_hline(yintercept=mean(Ros_BBChar$Mean),linetype="dashed")+
   labs(title="Biomass Burned and Charcoal Count - Rosalia",x="Age(yrs cal. BP)",y="RegBB (no unit)") +
   scale_y_continuous(name = "BB (no unit)",sec.axis = sec_axis(trans=~., name="Charcoal count (#)"))+
   theme(text=element_text(family="Times",size=12)) 
BBRosalia_plot
```

# *Fire Frequency*
```{r }
FF<-read.csv("Fire_histories/FF_Reg.csv",h=T,sep=",")
FF$Age<-as.numeric(FF$Age)
FF[916:1118,4]<-NA
colnames(FF)<-c("Age","Pikku","Charly","Rosalia","Mean")
Events<-read.csv("Fire_histories/Fire_events.csv",h=T,sep=";") 
mean(FF$Rosalia,na.rm=T)

FFRosalia_plot<-
ggplot(data=FF,aes(x=Age,y=Rosalia))+
    theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9052.5,32.5))+
   geom_hline(yintercept=mean(FF$Rosalia,na.rm=T),linetype="dashed")+
   scale_y_continuous(limits=c(0.0015,0.0056))+
   geom_line(size=1,color="red4")+
   annotate("point", x = Events[1:39,1], y = rep(0.0055,39), colour = "black")+
   labs(x="Age(yrs cal. BP)",y="FF (fire year-1)",title="Fire frequency - Rosalia")+
   theme(text=element_text(family="Times",size=12)) 
FFRosalia_plot
```

# *Fire Size*
```{r }
FS<-read.csv("Fire_histories/FS_Reg.csv",h=T,sep=",")
FS$Age<-as.numeric(FS$Age)

colnames(FS)<-c("Age","Mean","Charly","Rosalia","Pikku")  
FS[c(1:21,916:nrow(FS)),c(2:5)]<-NA
mean(FS$Rosalia,na.rm=T)
mean(FS$Pikku,na.rm=T)

FSRosalia_plot<-
ggplot(data=FS,aes(x=Age,y=Rosalia))+
   theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9052.5,32.5))+
   geom_hline(yintercept=mean(FS$Rosalia,na.rm=T),linetype="dashed")+   
   scale_y_continuous(limits=c(0.5,5))+
   geom_line(size=1,color="red4")+
   labs(x="Age(yrs cal. BP)",y="FS index (no unit)",title="FS index - Rosalia")+
   theme(text=element_text(family="Times",size=12)) 
FSRosalia_plot
```   

# *Charcoal aspect*
```{r }
Ros<-read.csv("Fire_histories/Rosalia_individual_charcoal.csv",head=T,sep=";")
Ros_BB<-read.csv("Fire_histories/Count_Rosalia.csv",head=T,sep=";")
colnames(Ros_BB)[1]<-"SampleId"
Ros_BB<-Ros_BB[,c(1,3)]
Ros_T<-merge(Ros,Ros_BB,by="SampleId")
colnames(Ros_T)[24]<-"Age"
Ros_T<-Ros_T[,c(24,5,7)]
Ros_T<-cbind(Ros_T[,1],Ros_T[,2]/Ros_T[,3])
Ros_T<-data.frame(Ros_T)
colnames(Ros_T)<-c("Age","LW")

LWRosalia_plot<-
ggplot(data=Ros_T,aes(x=Age,y=LW))+
   theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9052.5,32.5))+
   scale_y_log10("y",limits = c(1e0,3e1))+
   geom_point(aes(x=Age,y=LW),colour="grey40",size=0.8)+
   geom_smooth(span=0.3,color="red4",size=1)+
   geom_hline(yintercept=c(2.5))+
   geom_hline(yintercept=c(3.5))+
   labs(x="Age(yrs cal. BP)",y="Charcoal aspect (log10 LW ratio)",title="Charcoal aspect - Rosalia") +
   theme(text=element_text(family="Times",size=12)) 
LWRosalia_plot
```  



## **Pikku**
# *Biomass burned*
```{r }
Char_Pik<-read.csv("Fire_histories/Count_Pikku.csv",h=T,sep=";")[,c(3,4,6)]
colnames(Char_Pik)<-c("AgeTop","AgeBot","Count")

DF<-c()
for (i in 1:nrow(Char_Pik)){
Age<-seq(Char_Pik[i,1],Char_Pik[i,2],0.5)
CBind<-cbind(Age[1:c(length(Age)-1)],rep(Char_Pik[i,3],c(length(Age)-1)))
DF<-rbind(DF,CBind)
}
colnames(DF)<-c("Age","Count")

BB<-read.csv("Fire_histories/BB_Reg.csv",h=T,sep=",")
BB_Pikku<-read.csv("Fire_histories/BBPikku.csv",h=T,sep=",")[,c(1,2)]
colnames(BB_Pikku)<-c("Age","MeanR")
BB_Pikku$Age<-as.numeric(BB_Pikku$Age)
BB_Pikku[918:1118,2]<-NA

Pik_BBChar<-merge(DF,BB_Pikku,by="Age")
Pik_BBChar<-na.omit(Pik_BBChar)

colnames(Pik_BBChar)<-c("Age","Count","Mean")
Pik_BBChar[,3]<-rescale(Pik_BBChar[,3], to=c(min(Pik_BBChar$Count),max(Pik_BBChar$Count)))
Pik_BBChar<-as.data.frame(Pik_BBChar)
Pik_BBChar$Age<-as.numeric(Pik_BBChar$Age)

BBPikku_plot<-
ggplot(data=Pik_BBChar,aes(x=Age))+
theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9046,-34))+
   geom_line(aes(x=Age,y=Mean),size=1,color="red4")+
   geom_bar(aes(x=Age,y=Count),stat="identity", na.rm = TRUE)+
   geom_hline(yintercept=mean(Pik_BBChar$Mean),linetype="dashed")+
   labs(title="Biomass Burned and Charcoal Count - Pikku",x="Age(yrs cal. BP)",y="RegBB (no unit)") +
   scale_y_continuous(name = "BB (no unit)",sec.axis = sec_axis(trans=~., name="Charcoal count (#)"))+
   theme(text=element_text(family="Times",size=12)) 
BBPikku_plot
```

# *Fire Frequency*
```{r }
FF<-read.csv("Fire_histories/FF_Reg.csv",h=T,sep=",")
FF$Age<-as.numeric(FF$Age)
FF[916:1118,4]<-NA
colnames(FF)<-c("Age","Pikku","Charly","Rosalia","Mean")
Events<-read.csv("Fire_histories/Fire_events.csv",h=T,sep=";") 
mean(FF$Pikku,na.rm=T)

FFPikku_plot<-
ggplot(data=FF,aes(x=Age,y=Pikku))+
    theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9046,-34))+
   scale_y_continuous(limits=c(0.0015,0.0056))+
   geom_line(size=1,color="red4")+
   geom_hline(yintercept=mean(FF$Pikku,na.rm=T),linetype="dashed")+
   annotate("point", x = Events[1:35,2], y = rep(0.0056,35), colour = "black")+
   labs(x="Age(yrs cal. BP)",y="FF (fire year-1)",title="Fire frequency - Pikku")+
   theme(text=element_text(family="Times",size=12)) 
FFPikku_plot
```

# *Fire Size*
```{r }
FS<-read.csv("Fire_histories/FS_Reg.csv",h=T,sep=",")
FS$Age<-as.numeric(FS$Age)

colnames(FS)<-c("Age","Mean","Charly","Rosalia","Pikku")  
FS[c(1:21,916:nrow(FS)),c(2:5)]<-NA
mean(FS$Rosalia,na.rm=T)
mean(FS$Pikku,na.rm=T)

FSPikku_plot<-
ggplot(data=FS,aes(x=Age,y=Pikku))+
   theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9046,-34))+
   geom_hline(yintercept=mean(FS$Pikku,na.rm=T),linetype="dashed")+   
   scale_y_continuous(limits=c(0.5,5))+
   geom_line(size=1,color="red4")+
   labs(x="Age(yrs cal. BP)",y="FS index (no unit)",title="FS index - Pikku")+
   theme(text=element_text(family="Times",size=12)) 
FSPikku_plot
```   

# *Charcoal aspect*
```{r }
Pik<-read.csv("Fire_histories/Pikku_individual_charcoal.csv",head=T,sep=";")
Pik_BB<-read.csv("Fire_histories/Count_Pikku.csv",head=T,sep=";")
colnames(Pik_BB)[1]<-"SampleId"
Pik_BB<-Pik_BB[,c(1,3)]
Pik_T<-merge(Pik,Pik_BB,by="SampleId")
colnames(Pik_T)[24]<-"Age"
Pik_T<-Pik_T[,c(24,5,7)]
Pik_T<-cbind(Pik_T[,1],Pik_T[,2]/Pik_T[,3])
Pik_T<-data.frame(Pik_T)
colnames(Pik_T)<-c("Age","LW")


LWPikku_plot<-
ggplot(data=Pik_T,aes(x=Age,y=LW))+
   theme_classic()+ 
   scale_x_reverse(breaks =seq(0,100000,1000),limits=c(9046,-34))+
   scale_y_log10("y",limits = c(1e0,3e1))+
   geom_point(aes(x=Age,y=LW),colour="grey40",size=0.8)+
   geom_smooth(span=0.3,color="red4",size=1)+
   geom_hline(yintercept=c(2.5))+
   geom_hline(yintercept=c(3.5))+
   labs(x="Age(yrs cal. BP)",y="Charcoal aspect (log10 LW ratio)",title="Charcoal aspect - Pikku") +
   theme(text=element_text(family="Times",size=12)) 
LWPikku_plot
``` 
